\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2019-01-18 bare_conf.tex
Update bare_conf.tex
The 2 versions of affilations are added, PDF file was not generated

\author{
\begin{tabular}[t]{c@{\extracolsep{2em}}c} 
Povilas Daniu\v{s}is & Andrius Budrionis \\
{\scriptsize Department of Business Technologies  and Entrepreneurship }& {\scriptsize Norwegian Centre for E-health Research}\\ 
{\scriptsize Vilnius Gediminas Technical University} & {\scriptsize University Hospital of North Norway}\\
{\scriptsize Vilnius, Lithuania} & {\scriptsize Troms\o, Norway}\\
{\scriptsize email: povilas.daniusis@vgtu.lt} & {\scriptsize email: andrius.budrionis@vgtu.lt} \\
& \\
Audrius Indriulionis & Darius Plikynas \\
{\scriptsize Department of Business Technologies and Entrepreneurship} & {\scriptsize Department of Business Technologies and Entrepreneurship}\\ 
{\scriptsize Vilnius Gediminas Technical University} & {\scriptsize Vilnius Gediminas Technical University}\\
{\scriptsize Vilnius, Lithuania} & {\scriptsize Vilnius, Lithuania}\\
{\scriptsize email: audrius.indriulionis@vgtu.lt} & {\scriptsize email: darius.plikynas@vgtu.lt} \\
\end{tabular}
}

>>>>

% first version of affilation
%\author{\IEEEauthorblockN{Povilas Daniu\v{s}is\IEEEauthorrefmark{1},
%Andrius Budrionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
%Audrius Indriulionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{3} and 
%Darius Plikynas\IEEEauthorrefmark{1}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1} Department of Business Technologies  and Entrepreneurship\\ Vilnius Gediminas Technical University\\
%Vilnius, Lithuania}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Norwegian Centre for E-health Research\\ University %Hospital of North Norway\\
%Troms\o, Norway}
%\IEEEauthorblockA{\IEEEauthorrefmark{3} Laboratory of Quaternary Research\\ Nature Research Centre %\\ Vilnius, Lithuania\\
%Email: \IEEEauthorrefmark{1} {povilas.daniusis, andrius.budrionis, audrius.indriulionis, %darius.plikynas} @vgtu.lt}}

%%%%\IEEEauthorrefmark{2}andrius.budrionis@vgtu.lt,
%%%%\IEEEauthorrefmark{3}audrius.indriulionis@vgtu.lt,
%%%\\\IEEEauthorrefmark{4}darius.plikynas@vgtu.lt}}
% second version of affilation
\author[1]{Povilas Daniu\v{s} Darius Plikynas}
\author[1,2]{Andrius Budrionis}
\author[1,3]{ Audrius Indriulionis}
\affil[1]{Department of Business Technologies  and Entrepreneurship 
\authorcr Gediminas Technical University 
\authorcr Vilnius, Lithuania
\authorcr Email: {\tt \{povilas.daniusis, darius.plikynas\}@vgtu.lt}\vspace{1.5ex}}
\affil[2]{Norwegian Centre for E-health Research 
\authorcr University Hospital of North Norway
\authorcr Troms\o, Norway
 \authorcr Email: {\tt andrius.budrionis@ehealthresearch.no} \vspace{1.5ex}} 
\affil[3]{Laboratory of Quaternary Research 
\authorcr  Nature Research Centre
\authorcr Vilnius, Lithuania
\authorcr Email: {\tt audrius.indriulionis@gmail.com}}
